### 2019-02-26 sections/example.tex
describe all, any, intersect, difference
briefly explain Enter

The requirements of the application are as follows.
\begin{enumerate*}
  \item A user has to enter a list of passengers for which to book tickets.
  \item At least one of these passengers has to be an adult.
  \item After a valid list of passengers has been entered, the user has to pick seats.
  \item Only free seats may be picked.
  \item Every passenger must have exactly one seat.
  \item Multiple users should be able to book tickets at the same time.
\end{enumerate*}
For this example we assume that the host language has lists and four functions on them: all, any, intersect, and difference. \fixme{Alejandro: small description may be needed} %nico: of the functions
%%NOTE: After Peter's comments symbols are not clear --TS
We also make use of string equality ($\equiv$), dereferencing ($!$), reference assignment ($:=$), and expression sequencing ($;$).
For brevity, we omit the type annotations of variable bindings.

@@

Now we develop our workflow in a top down way.
A flight booking starts with an interactive task \TS{enter (List Passenger)}
where users can enter a list of passengers.
A passenger is valid if the name is not empty and the age is at least 0.
A list of passengers is valid if each passenger is valid, and at least one of the passengers is an adult.
When the user has entered a valid list of passengers, the step after \TS{>>?} becomes enabled,
and the user can proceed to picking seats.
\begin{TASK}
  let valid = \p. not (fst p == "") /\ snd p >= 0 in
  let adult = \p. snd p >= 18 in
  let allValid = \ps. all valid ps /\ any adult ps in
  let bookFlight = enter (List Passenger) >>? \ps.
    if allValid ps then chooseSeats ps else fail
\end{TASK}
\fixme{Alejandro: At this point I wonder, what is $\Enter$}
A selection of seats is correct if every entered seat is free.
\begin{TASK}
  let correct = \ss. intersect ss !freeSeats == ss in
  let chooseSeats = \ps. enter (List Seat) >>? \ss.
    if correct ss /\ length ps == length ss then confirmBooking ps ss else fail
\end{TASK}

>>>>

The requirements of the application are as follows.
\begin{enumerate*}
  \item A user has to enter a list of passengers for which to book tickets.
  \item At least one of these passengers has to be an adult.
  \item After a valid list of passengers has been entered, the user has to pick seats.
  \item Only free seats may be picked.
  \item Every passenger must have exactly one seat.
  \item Multiple users should be able to book tickets at the same time.
\end{enumerate*}
For this example we assume that the host language has lists and four functions on them: all, any, intersect, and difference.
The functions all and any check if all or any elements in a list satisfy a given predicate.
The functions intersect and difference compute the set-intersection and set-difference of two lists.
%%NOTE: After Peter's comments symbols are not clear --TS
We also make use of string equality ($\equiv$), dereferencing ($!$), reference assignment ($:=$), and expression sequencing ($;$).
For brevity, we omit the type annotations of variable bindings.

@@

Now we develop our workflow in a top down way.
A flight booking starts with an interactive task \TS{enter (List Passenger)}
where users can enter a list of passengers.
A passenger is valid if the name is not empty and the age is at least 0.
A list of passengers is valid if each passenger is valid, and at least one of the passengers is an adult.
When the user has entered a valid list of passengers, the step after \TS{>>?} becomes enabled,
and the user can proceed to picking seats.
The task $\Enter$ is an empty editor that asks for a value of the given type.
\begin{TASK}
  let valid = \p. not (fst p == "") /\ snd p >= 0 in
  let adult = \p. snd p >= 18 in
  let allValid = \ps. all valid ps /\ any adult ps in
  let bookFlight = enter (List Passenger) >>? \ps.
    if allValid ps then chooseSeats ps else fail
\end{TASK}
A selection of seats is correct if every entered seat is free.
\begin{TASK}
  let correct = \ss. intersect ss !freeSeats == ss in
  let chooseSeats = \ps. enter (List Seat) >>? \ss.
    if correct ss /\ length ps == length ss then confirmBooking ps ss else fail
\end{TASK}
